---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# nawtilus: An R Package for the Navigated Weighting (NAWT)

<!-- badges: start -->
<!-- badges: end -->

**nawtilus** provides a procedure for the navigated weighting (nawt), which estimates a pre-specified parameter of interest (e.g., the average treatment effects or the average treatment effects on the treated) with the inverse probability weighting where propensity scores are estimated using estimating equations suitable for the parameter of interest. It also provides several tools for summarizing and checking the estimation results, including covariate balance check and an inverse probability weights plot.

## Installation

<!--
You can install the released version of nawtilus from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("nawtilus")
```

And the development version from [GitHub](https://github.com/) with:
-->

You can install the development version from [GitHub](https://github.com/) with:
``` r
# install.packages("devtools")
devtools::install_github("hirotokatsumata/nawtilus")
```
## Example

This example shows how to use **nawtilus** for estimation of parameter of interest.

First, load the package and make toy data.
```{r data}
# Load the function
library(nawtilus)

# Make toy data
# ATT estimation
# True ATT is 10
tau <- 10
set.seed(12345)
n <- 1000
X <- matrix(rnorm(n * 4, mean = 0, sd = 1), nrow = n, ncol = 4)
prop <- 1 / (1 + exp(X[, 1] - 0.5 * X[, 2] + 0.25 * X[, 3] + 0.1 * X[, 4]))
treat <- rbinom(n, 1, prop)
y <- 210 + 27.4 * X[, 1] + 13.7 * X[, 2] + 13.7 * X[, 3] + 13.7 * X[, 4] + 
     tau * treat + rnorm(n)

# Data frame
df <- data.frame(X, treat, y)
colnames(df) <- c("x1", "x2", "x3", "x4", "treat", "y")
```

Then, specify a model for propensity score estimation.
```{r formula}
formula_c <- as.formula(treat ~ x1 + x2 + x3 + x4)
```

Fit the model for the average treatment effects on the treated (ATT) estimation using `nawt()` with the default setting (a power weighting function with &alpha; = 2).
```{r nawt}
# Power weighting function with alpha = 2
fit <- nawt(formula = formula_c, outcome = "y", estimand = "ATT", 
            method = "score", data = df, alpha = 2)
```

You can summarize the results easily with `summary()`.
```{r summary.nawt}
summary(fit)
```

Check covariate balance between the treatment and control groups before and after the nawt with `cbcheck()`.
```{r cbcheck, fig.align = 'center', fig.width = 7, fig.height = 7, out.width = 600, out.height = 600}
oldpar <- par(no.readonly = TRUE)
par(mar = c(5.1, 5.1, 4.1, 2.1))
cbcheck(fit)
par <- oldpar
```

Let's compare the inverse probability weights estimated by the nawt with those estimated by the standard logistic regression with `plot()`.
```{r plot.nawt, fig.align = 'center', fig.width = 7, fig.height = 7, out.width = 600, out.height = 600}
plot(fit)
```

Finally, check the weights used in propensity score estimation and distribution of the estimated propensity scores in the nawt with `plot_onega()`.
```{r plot_omega, fig.align = 'center', fig.width = 7, fig.height = 7, out.width = 600, out.height = 600}
plot_omega(fit)
```
